Defining properties regulating pioneer-factor binding and function

### 2023-01-10 manuscript/manuscript_sections/_06_Figure_Legends.qmd
add code for supp figs 2-4

-   Western blot time course of protein levels

@@

-   RNA-seq volcano/MA plots

-   RNA-seq GO analysis

@@

@@

-   TWI RNA-seq volcano and examples

-   Twi RNA-seq GO analysis

>>>>

-   ~~Western blot time course of protein levels~~

@@

-   ~~RNA-seq volcano/MA plots~~

-   ~~RNA-seq GO analysis~~

-   Genome browser examples of specific and nonspecific accessibility changes?

-   motif enrichment for nonspecific changes?

-   \% of TFs bound and activated by Zld/Grh as indicator of nonspecific changes?

-   Should we include any analysis of decreased/downregulated sites for RNA-seq or ATAC?

-   Violin plots to emphasize correlation between ATAC and RNA-seq?

@@

-   Western blot of Twi induction

@@

-   ~~TWI RNA-seq volcano and examples3~~

-   ~~Twi RNA-seq GO analysis~~

-   Genome browser examples of specific and nonspecific accessibility changes?

-   motif enrichment for nonspecific changes?

-   \% of TFs bound and activated by Zld/Grh as indicator of nonspecific changes?

-   Should we include any analysis of decreased/downregulated sites for RNA-seq or ATAC?

-   Violin plots to emphasize correlation between ATAC and RNA-seq?
